---
title: "Data Detective: Dataset Investigation Report"
subtitle: "Automated Statistical Data Quality & Exploratory Analysis"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S %Z')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
params:
  file_name: "dataset.csv"
  profile: NULL
  quality_info: NULL
  missing_info: NULL
  duplicate_info: NULL
  outlier_info: NULL
  constant_info: NULL
  correlation_info: NULL
  leakage_info: NULL
  representation_info: NULL
  findings_result: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Dataset Overview

- **Source File:** `r params$file_name`
- **Total Rows:** `r if (!is.null(params$profile)) format(params$profile$n_rows, big.mark = ",") else "0"`
- **Total Columns:** `r if (!is.null(params$profile)) format(params$profile$n_cols, big.mark = ",") else "0"`
- **Memory Footprint:** `r if (!is.null(params$profile)) params$profile$memory_formatted else "0 B"`

---

## 1. Executive Summary

`r if (!is.null(params$findings_result)) params$findings_result$executive_summary else "No executive summary available."`

---

## 2. Data Quality Indicator

```{r quality_summary}
if (!is.null(params$quality_info)) {
  cat(paste0("**Data Quality Score:** ", params$quality_info$score, " / 100\n\n"))
  cat(paste0("**Status:** ", params$quality_info$status, "\n\n"))
  cat(paste0("*", params$quality_info$explanation, "*\n\n"))
}
```

---

## 3. Dataset Profile & Summary Statistics

```{r profile_table}
if (!is.null(params$profile) && nrow(params$profile$columns_summary) > 0) {
  knitr::kable(params$profile$columns_summary[, c("column", "data_type", "missing_count", "missing_pct", "unique_count", "min", "max", "mean")],
               caption = "Dataset Variable Profile")
}
```

---

## 4. Missing Value Diagnostics

```{r missing_summary}
if (!is.null(params$missing_info) && nrow(params$missing_info$column_summary) > 0) {
  m_sub <- params$missing_info$column_summary[params$missing_info$column_summary$missing_count > 0, ]
  if (nrow(m_sub) > 0) {
    knitr::kable(m_sub, caption = "Columns with Missing Values")
  } else {
    cat("No missing values were detected in any column.\n")
  }
}
```

---

## 5. Duplicate Records Assessment

```{r duplicate_summary}
if (!is.null(params$duplicate_info)) {
  cat(paste0("- **Total Exact Duplicate Rows:** ", params$duplicate_info$duplicate_rows_count, " (", params$duplicate_info$duplicate_pct, "%)\n"))
  cat(paste0("- **Unique Records:** ", params$duplicate_info$unique_rows_count, "\n"))
  cat(paste0("- **Status:** ", params$duplicate_info$status, "\n"))
}
```

---

## 6. Outlier Investigation (IQR Method)

```{r outlier_summary}
if (!is.null(params$outlier_info) && nrow(params$outlier_info$summary) > 0) {
  knitr::kable(params$outlier_info$summary[, c("column", "q1", "q3", "iqr", "lower_bound", "upper_bound", "outlier_count", "outlier_pct")],
               caption = "Outlier Observations (IQR 1.5 Multiplier)")
}
```

---

## 7. Correlation & Multicollinearity

```{r correlation_summary}
if (!is.null(params$correlation_info) && nrow(params$correlation_info$multicollinear_pairs) > 0) {
  knitr::kable(params$correlation_info$multicollinear_pairs[, c("variable_a", "variable_b", "pearson_r", "strength", "investigation_note")],
               caption = "Highly Correlated Feature Pairs (|r| >= 0.70)")
} else {
  cat("No severe multicollinear pairs (|r| >= 0.70) detected.\n")
}
```

---

## 8. Potential Data Leakage & Representation Indicators

```{r leakage_rep}
if (!is.null(params$leakage_info) && params$leakage_info$target_specified && nrow(params$leakage_info$indicators) > 0) {
  knitr::kable(params$leakage_info$indicators, caption = "Potential Data Leakage Indicators")
}

if (!is.null(params$representation_info) && nrow(params$representation_info$indicators) > 0) {
  knitr::kable(params$representation_info$indicators, caption = "Potential Representation Disparities")
}
```

---

## 9. Comprehensive Investigation Findings

```{r findings_table}
if (!is.null(params$findings_result) && nrow(params$findings_result$findings) > 0) {
  knitr::kable(params$findings_result$findings[, c("id", "category", "severity", "column", "description", "evidence", "recommendation")],
               caption = "Complete Investigation Findings Dossier")
} else {
  cat("No investigation flags were triggered for this dataset.\n")
}
```

---

## 10. Recommended Investigation Steps

1. **Review High-Severity Flags:** Prioritize reviewing columns with critical missingness and potential leakage indicators.
2. **Examine Outlier Origins:** Distinguish measurement errors from genuine tail phenomena.
3. **Address Redundancy:** Review multicollinear features prior to linear statistical estimation.
4. **Inspect Group Disparities:** Check representation balance across demographic or transactional cohorts.

---

> **Report Disclaimer:**
> This report is an automated statistical investigation. Detected patterns are indicators for further investigation and should not automatically be interpreted as data errors, causal relationships, confirmed leakage, or confirmed bias.
